Predicting sales of newly published books

### 2015-08-23 paper.tex
arreglando un error de compilación

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%%
\author {
P.A. Castillo, A.M. Mora, J.J. Merelo,  et al.
}
\institute{Department of Architecture and Computer Technology. CITIC \\
           University of Granada (Spain) \\
~\\
           e-mail: {\tt pacv@ugr.es}}

@@

Experiments have been conducted on an Intel(R) Core(TM) i5-4430 CPU at 3.00GHz 
(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE_1.7.0_72.

>>>>

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%%
\author {
P.A. Castillo, A.M. Mora, J.J. Merelo, \\ A.J. Fern\'andez-Ares, P. Garc\'{\i}a-S\'anchez, M.G. Arenas
}
\institute{Department of Architecture and Computer Technology. CITIC \\
           University of Granada (Spain) \\
~\\
           e-mail: {\tt pacv@ugr.es}}

@@

Experiments have been conducted on an Intel(R) Core(TM) i5-4430 CPU at 3.00GHz 
(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE\_1.7.0\_72.
